\hypertarget{namespace_badges___issuer___for___wp}{}\section{Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp Namespace Reference}
\label{namespace_badges___issuer___for___wp}\index{Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp@{Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp}}


\subsection{Detailed Description}
The admin-\/specific functionality of the plugin.

\hyperlink{}{1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/admin The admin-\/specific functionality of the plugin. Defines the plugin name, version, and two examples hooks for how to enqueue the admin-\/specific stylesheet and Java\+Script.  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/admin  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} Provide a admin area view for the plugin This file is used to markup the admin-\/facing aspects of the plugin.  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/admin/partials The plugin bootstrap file This file is read by Word\+Press to generate the plugin information in the plugin admin area. This file also includes all of the dependencies used by the plugin, registers the activation and deactivation functions, and defines a function that starts the plugin.  www.\+badges4languages.\+com  1.\+0.\+0 -\/plugin Plugin Name\+: Badges-\/\+Issuer-\/for-\/wp Plugin U\+R\+I\+: www.\+badges4languages.\+com Description\+: This is a short description of what the plugin does. It\textquotesingle{}s displayed in the Word\+Press admin area. Version\+: 1.\+0.\+0 Author\+: My language skills team Author U\+R\+I\+: www.\+badges4languages.\+com License\+: G\+P\+L-\/2.\+0+ License U\+R\+I\+: \href{http://www.gnu.org/licenses/gpl-2.0.txt}{\tt http\+://www.\+gnu.\+org/licenses/gpl-\/2.\+0.\+txt} Text Domain\+: badges-\/issuer-\/for-\/wp Domain Path\+: /languages Fired during plugin activation  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes Fired during plugin activation. This class defines all code necessary to run during the plugin\textquotesingle{}s activation.  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} Fired during plugin deactivation  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes Fired during plugin deactivation. This class defines all code necessary to run during the plugin\textquotesingle{}s deactivation.  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} Define the internationalization functionality Loads and defines the internationalization files for this plugin so that it is ready for translation.  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes Define the internationalization functionality. Loads and defines the internationalization files for this plugin so that it is ready for translation.  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} Register all actions and filters for the plugin  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes Register all actions and filters for the plugin. Maintain a list of all hooks that are registered throughout the plugin, and register them with the Word\+Press A\+PI. Call the run function to execute the list of actions and filters.  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} The file that defines the core plugin class A class definition that includes attributes and functions used across both the public-\/facing side of the site and the admin area.  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes The core plugin class. This is used to define internationalization, admin-\/specific hooks, and public-\/facing site hooks. Also maintains the unique identifier of this plugin as well as the current version of the plugin.  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/includes  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} The public-\/facing functionality of the plugin.  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/public The public-\/facing functionality of the plugin. Defines the plugin name, version, and two examples hooks for how to enqueue the admin-\/specific stylesheet and Java\+Script.  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/public  My language skills team \href{mailto:mylanguageskills@hotmail.com}{\tt mylanguageskills@hotmail.\+com} Provide a public-\/facing view for the plugin This file is used to markup the public-\/facing aspects of the plugin.  www.\+badges4languages.\+com  1.\+0.\+0  Badges\+\_\+\+Issuer\+\_\+\+For\+\_\+\+Wp/public/partials Fired when the plugin is uninstalled. When populating this file, consider the following flow of control\+: This method should be staticCheck if the \$\+\_\+\+R\+E\+Q\+U\+E\+ST content actually is the plugin nameRun an admin referrer check to make sure it goes through authenticationVerify the output of \$\+\_\+\+G\+ET makes senseRepeat with other user roles. Best directly by using the links/query string parameters.Repeat things for multisite. Once for a single site in the network, once sitewide. This file may be updated more in future version of the Boilerplate; however, this is the general skeleton and outline for how the file should work. For more information, see the following discussion\+: \href{https://github.com/tommcfarlin/WordPress-Plugin-Boilerplate/pull/123#issuecomment-28541913}{\tt https\+://github.\+com/tommcfarlin/\+Word\+Press-\/\+Plugin-\/\+Boilerplate/pull/123\#issuecomment-\/28541913}  www.\+badges4languages.\+com  1.\+0.\+0 }